### 2015-09-14 Manuscript/SW_early_life_telomeres_v9.Rmd
Test from home laptop

#####Statistical analyses
We performed all analyses using R version 3.0.1 [@RDevelopmentCoreTeam2011]. Our sampling regime covers a long time-period, and temporal variation in rainfall and food availability on Cousin may cause variation  in a range of social and evironmental variables [@Brouwer2012]. This makes it difficult to disentangle how spatial and temporal social and environmental variation affects early-life telomere dynamics. we seperately analysed how variation in early life conditions among and within breeding seasons was related to variation in early life telomere length.  First, we tested whether there was a temporal effect on telomere lengthby calculating average telomere length among all birds born in a given breeding season. We tested for a difference in amomg breeding seasons using a one-way ANOVA, and then used linear regression to test whether variation in mean telomere length among breeding seasons is explained by temporal variation in insect abundance.

>>>>

#####Statistical analyses
We performed all analyses using R version 3.0.1 [@RDevelopmentCoreTeam2011]. Our sampling regime covers `r max(juv$LayYear)-min(juv$LayYear)` years, and temporal variation in rainfall and food availability on Cousin may cause variation  in a range of social and evironmental variables [@Brouwer2012]. This makes it difficult to disentangle how spatial and temporal social and environmental variation affects early-life telomere dynamics. we seperately analysed how variation in early life conditions among and within breeding seasons was related to variation in early life telomere length.  First, we tested whether there was a temporal effect on telomere lengthby calculating average telomere length among all birds born in a given breeding season. We tested for a difference in amomg breeding seasons using a one-way ANOVA, and then used linear regression to test whether variation in mean telomere length among breeding seasons is explained by temporal variation in insect abundance.
